Derivation of Variational Bayes

### 2016-08-03 written report/2levelmixture.tex
First

\documentclass[12pt]{article}
\usepackage{natbib}
\usepackage{color}
\usepackage[dvipsnames,svgnames*]{xcolor}
\usepackage{array}
\usepackage[colorlinks=TRUE, linkcolor=blue]{hyperref}
\usepackage[font=small,skip=5pt]{caption}
\usepackage[aboveskip=2pt]{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{ulem}
\usepackage{afterpage}
\usepackage{bbm}

\graphicspath{{images/}}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\begin{document}

@@

The quantity $\tilde{\pi}_1 = \mathbb{E}_\pi \ln(\pi) = \psi(\alpha)-\psi(\alpha+\beta)$, and $\tilde{\pi}_2 = \mathbb{E}_\pi \ln(1-\pi) = \psi(\beta)-\psi(\alpha+\beta)$, where $\psi(\cdot)$ is the digamma function (Archambeau and Verleysen 2007).

@@

\begin{eqnarray*}
\alpha & = & \sum_{i=1}^{n} \frac{p_i}{p_i+q_i} + 1 \\
\beta & = & \sum_{i=1}^{n} \frac{q_i}{p_i+q_i} + 1 \\
\bar{\mu}_1 & = &  \frac{\sum_{i=1}^{n} y_i p_i /(p_i+q_i)}{\sum_{i=1}^{n} p_i /(p_i+q_i)} \\
\lambda_1 & = & \left(\sum_{i=1}^{n} \frac{p_i}{p_i+q_i}\right)^{-1} \\
\bar{\mu}_2 & = &  \frac{\sum_{i=1}^{n} y_i q_i /(p_i+q_i)}{\sum_{i=1}^{n} q_i /(p_i+q_i)} \\
\lambda_2 & = & \left(\sum_{i=1}^{n} \frac{q_i}{p_i+q_i}\right)^{-1} \\
p_i & = & \exp \left\{\frac{2(\psi(\alpha)-\psi(\alpha+\beta))-((y_i - \bar{\mu}_1)^2 + \lambda_1)}{2} \right\} \\
q_i & = & \exp \left\{\frac{2(\psi(\beta)-\psi(\alpha+\beta))-((y_i - \bar{\mu}_2)^2 + \lambda_2)}{2} \right\}
\end{eqnarray*}

<<vbayes, echo=FALSE>>=
library(ggplot2)
#True Values
set.seed(12)
mu1 <- 3
mu2 <- 6
pi <- 0.6
T <- 250
y1 <- rnorm(T*pi, mu1, 1)
y2 <- rnorm(T*(1-pi), mu2, 1)
y <- c(y1, y2)

#Setup
bmu1 <- vector(length=100)
bmu2 <- bmu1
l1 <- bmu1
l2 <- bmu1
a <- bmu1
b <- bmu1
p <- matrix(0, nrow=100, ncol=T)
q <- p

#Initial values
p0 <- runif(T)
q0 <- runif(T)

#Loop
a[1] = sum(p0/(p0+q0))+1
b[1] = sum(q0/(p0+q0))+1
bmu1[1] = sum(y*p0/(p0+q0))/sum(p0/(p0+q0))
l1[1] = sum(p0/(p0+q0))^(-1)
bmu2[1] = sum(y*q0/(p0+q0))/sum(q0/(p0+q0))
l2[1] = sum(q0/(p0+q0))^(-1)
for(j in 1:T){
  p[1,j] = exp((2*(digamma(a[1])-digamma(a[1]+b[1]))-((y[j]-bmu1[1])^2+l1[1]))/2)
  q[1,j] = exp((2*(digamma(b[1])-digamma(a[1]+b[1]))-((y[j]-bmu2[1])^2+l2[1]))/2)
}
for(i in 2:100) {
  a[i] = sum(p[(i-1),]/(p[(i-1),]+q[(i-1),]))+1
  b[i] = sum(q[(i-1),]/(p[(i-1),]+q[(i-1),]))+1
  bmu1[i] = sum(y*p[(i-1),]/(p[(i-1),]+q[(i-1),]))/sum(p[(i-1),]/(p[(i-1),]+q[(i-1),]))
  l1[i] = sum(p[(i-1),]/(p[(i-1),]+q[(i-1),]))^(-1)
  bmu2[i] = sum(y*q[(i-1),]/(p[(i-1),]+q[(i-1),]))/sum(q[(i-1),]/(p[(i-1),]+q[(i-1),]))
  l2[i] = sum(q[(i-1),]/(p[(i-1),]+q[(i-1),]))^(-1)
  for(j in 1:T){
    p[i,j] = exp((2*(digamma(a[i])-digamma(a[i]+b[i]))-((y[j]-bmu1[i])^2+l1[i]))/2)
    q[i,j] = exp((2*(digamma(b[i])-digamma(a[i]+b[i]))-((y[j]-bmu2[i])^2+l2[i]))/2)
  }
}
supmu1 <- seq(2, 4, 0.01)
denmu1 <- dnorm(supmu1, mean=bmu1[100], sd=sqrt(l1[100]))
supmu2 <- seq(5, 7, 0.01)
denmu2 <- dnorm(supmu2, mean=bmu2[100], sd=sqrt(l2[100]))
suppi <- seq(0, 1, 0.01)
denpi <- dbeta(suppi, a[100], b[100])
qdist <- data.frame(support = c(supmu1, supmu2, suppi), density = c(denmu1, denmu2, denpi), parameter = c(rep("Mu 1", 201), rep("Mu 2", 201), rep("Pi", 101)))
truev <- data.frame(true = c(mu1, mu2, pi), parameter=c("Mu 1", "Mu 2", "Pi"))
ggplot() + geom_line(data=qdist, aes(x=support, y = density)) + geom_vline(data=truev, aes(xintercept=true), colour="red") +
  facet_wrap(~parameter, scales="free") + theme(axis.ticks.y=element_blank(), axis.text.y=element_blank()) + theme_bw()
@
250 draws were simulated with parameters $\mu_1 = 3, \mu_2 = 6, \pi=0.6$ and th e variational algorithm was ran. After manually correcting mislabeling, $y_i$ was allocated to distribution 1 if $p_i > q_i$ and to distribution 2 if $p_i < q_i$, resulting in the successful classification of 235/250 draws. A more trivial decision rule to allocate $y_i$ to distribution 1 if $y_i < \bar{y}$ and to distribution 2 if $y_i > \bar{y}$ successfully classified 234/250 draws.

<<vbayes2, echo=FALSE>>=
library(ggplot2)
#True Values
set.seed(141242)
mu1 <- 5.5
mu2 <- 6
pi <- 0.6
T <- 250
y1 <- rnorm(T*pi, mu1, 1)
y2 <- rnorm(T*(1-pi), mu2, 1)
y <- c(y1, y2)

#Setup
bmu1 <- vector(length=100)
bmu2 <- bmu1
l1 <- bmu1
l2 <- bmu1
a <- bmu1
b <- bmu1
p <- matrix(0, nrow=100, ncol=T)
q <- p

#Initial values
p0 <- runif(T)
q0 <- runif(T)

#Loop
a[1] = sum(p0/(p0+q0))+1
b[1] = sum(q0/(p0+q0))+1
bmu1[1] = sum(y*p0/(p0+q0))/sum(p0/(p0+q0))
l1[1] = sum(p0/(p0+q0))^(-1)
bmu2[1] = sum(y*q0/(p0+q0))/sum(q0/(p0+q0))
l2[1] = sum(q0/(p0+q0))^(-1)
for(j in 1:T){
  p[1,j] = exp((2*(digamma(a[1])-digamma(a[1]+b[1]))-((y[j]-bmu1[1])^2+l1[1]))/2)
  q[1,j] = exp((2*(digamma(b[1])-digamma(a[1]+b[1]))-((y[j]-bmu2[1])^2+l2[1]))/2)
}
for(i in 2:100) {
  a[i] = sum(p[(i-1),]/(p[(i-1),]+q[(i-1),]))+1
  b[i] = sum(q[(i-1),]/(p[(i-1),]+q[(i-1),]))+1
  bmu1[i] = sum(y*p[(i-1),]/(p[(i-1),]+q[(i-1),]))/sum(p[(i-1),]/(p[(i-1),]+q[(i-1),]))
  l1[i] = sum(p[(i-1),]/(p[(i-1),]+q[(i-1),]))^(-1)
  bmu2[i] = sum(y*q[(i-1),]/(p[(i-1),]+q[(i-1),]))/sum(q[(i-1),]/(p[(i-1),]+q[(i-1),]))
  l2[i] = sum(q[(i-1),]/(p[(i-1),]+q[(i-1),]))^(-1)
  for(j in 1:T){
    p[i,j] = exp((2*(digamma(a[i])-digamma(a[i]+b[i]))-((y[j]-bmu1[i])^2+l1[i]))/2)
    q[i,j] = exp((2*(digamma(b[i])-digamma(a[i]+b[i]))-((y[j]-bmu2[i])^2+l2[i]))/2)
  }
}
supmu1 <- seq(5, 7, 0.01)
denmu1 <- dnorm(supmu1, mean=bmu1[100], sd=sqrt(l1[100]))
supmu2 <- seq(5, 7, 0.01)
denmu2 <- dnorm(supmu2, mean=bmu2[100], sd=sqrt(l2[100]))
suppi <- seq(0, 1, 0.01)
denpi <- dbeta(suppi, a[100], b[100])
qdist <- data.frame(support = c(supmu1, supmu2, suppi), density = c(denmu1, denmu2, denpi), parameter = c(rep("Mu 1", 201), rep("Mu 2", 201), rep("Pi", 101)))
truev <- data.frame(true = c(mu1, mu2, pi), parameter=c("Mu 1", "Mu 2", "Pi"))
ggplot() + geom_line(data=qdist, aes(x=support, y = density)) + geom_vline(data=truev, aes(xintercept=true), colour="red") +
  facet_wrap(~parameter, scales="free") + theme(axis.ticks.y=element_blank(), axis.text.y=element_blank()) + theme_bw()
@
250 draws were simulated with parameters $\mu_1 = 5.5, \mu_2 = 6, \pi=0.6$ to try and force an overlap in the data. $y_i$ was allocated to distribution 1 if $p_i > q_i$ and to distribution 2 if $p_i < q_i$, resulting in the successful classification of 158/250 draws. The trivial decision rule had identical classifications.

>>>>

\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{natbib}
\usepackage{color}
\usepackage[dvipsnames,svgnames*]{xcolor}
\usepackage{array}
\usepackage[colorlinks=TRUE, linkcolor=blue]{hyperref}
\usepackage[font=small,skip=5pt]{caption}
\usepackage[aboveskip=2pt]{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{ulem}
\usepackage{afterpage}
\usepackage{bbm}

\graphicspath{{images/}}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

The quantity $\tilde{\pi}_1 = \mathbb{E}_\pi \ln(\pi) = \psi(\alpha)-\psi(\alpha+\beta)$, and $\tilde{\pi}_2 = \mathbb{E}_\pi \ln(1-\pi) = \psi(\beta)-\psi(\alpha+\beta)$, where $\psi(\cdot)$ is the digamma function (Archambeau and Verleysen 2007). We also expanded the quadratic term and substitued in $(y_i^2 - \bar{\mu}_j)^2 + \lambda_j$ for $\mathbb{E} (y_i-\mu_j)^2$.

@@

\begin{eqnarray*}
a & = & \sum_{i=1}^{n} \frac{p_i}{p_i+q_i} + 1 \\
b & = & \sum_{i=1}^{n} \frac{q_i}{p_i+q_i} + 1 \\
\bar{\mu}_1 & = &  \frac{\sum_{i=1}^{n} y_i p_i /(p_i+q_i)}{\sum_{i=1}^{n} p_i /(p_i+q_i)} \\
\lambda_1 & = & \left(\sum_{i=1}^{n} \frac{p_i}{p_i+q_i}\right)^{-1} \\
\bar{\mu}_2 & = &  \frac{\sum_{i=1}^{n} y_i q_i /(p_i+q_i)}{\sum_{i=1}^{n} q_i /(p_i+q_i)} \\
\lambda_2 & = & \left(\sum_{i=1}^{n} \frac{q_i}{p_i+q_i}\right)^{-1} \\
p_i & = & \exp \left\{\frac{2(\psi(a)-\psi(a+b))-((y_i - \bar{\mu}_1)^2 + \lambda_1)}{2} \right\} \\
q_i & = & \exp \left\{\frac{2(\psi(b)-\psi(a+b))-((y_i - \bar{\mu}_2)^2 + \lambda_2)}{2} \right\}
\end{eqnarray*}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/vbayes-1}

\end{knitrout}
250 draws were simulated with parameters $\mu_1 = 3, \mu_2 = 6, \pi=0.6$ and th e variational algorithm was ran. After manually correcting mislabeling, $y_i$ was allocated to distribution 1 if $p_i > q_i$ and to distribution 2 if $p_i < q_i$, resulting in the successful classification of 235/250 draws. A more trivial decision rule to allocate $y_i$ to distribution 1 if $y_i < \bar{y}$ and to distribution 2 if $y_i > \bar{y}$ successfully classified 234/250 draws.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/vbayes2-1}

\end{knitrout}
250 draws were simulated with parameters $\mu_1 = 5.5, \mu_2 = 6, \pi=0.6$ to try and force an overlap in the data. $y_i$ was allocated to distribution 1 if $p_i > q_i$ and to distribution 2 if $p_i < q_i$, resulting in the successful classification of 158/250 draws. The trivial decision rule had identical classifications.

### 2016-08-03 written report/ar1_predictive.tex
First

\documentclass{article}
\usepackage{natbib}
\usepackage{color}
\usepackage[dvipsnames,svgnames*]{xcolor}
\usepackage{array}
\usepackage[colorlinks=TRUE, linkcolor=blue]{hyperref}
\usepackage{wrapfig,float}
\usepackage[font=small,skip=5pt]{caption}
\usepackage[aboveskip=2pt]{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{ulem}
\usepackage[section]{placeins}
\usepackage{afterpage}
\usepackage{bbm}
\begin{document}
\SweaveOpts{concordance=TRUE}

Note: Code uses a stretched beta, latex math still uses regular beta.

@@

<<forecast, echo=FALSE>>=
##One step variational forecast
library(Rcpp)
library(tidyr)
library(ggplot2)
library(dplyr)
library(RcppArmadillo)
sourceCpp("AR1c.cpp")
library(truncnorm)
library(flexmix)

set.seed(100)
T <- 100
tmu <- 3
tpsi <- 0.5
tsig <- 1
y <- tmu + arima.sim(list(ar=c(tpsi)), T, sd=tsig)

#Empty vectors
N <- 500
barmu = vector(length=N)
lambda = vector(length=N)
hatpsi = vector(length=N)
gamma = vector(length=N)
a = vector(length=N)
b = vector(length=N)
yhat = vector(length=N)
d = vector(length=N)

b0 = 1
a0 = 1
yhat0 = 1
psi0 = 0.8
gamma0 = 1
barmu0 = 1
lambda0 = 1
d0 = 1
p1 = 2
p2 = 3

#psi kernel function
psi.k <- function(psi, y, a, b, yhat, mu, p1, p2) {
  psibar = (sum(y[2:T]*y[1:T-1])+yhat*y[T]-mu*sum(y))/sum(y^2)
  out = sum(y^2)*(-b/a)*(psi-psibar)^2+(p1-1)*log(psi)+(p2-1)*log(1-psi)
  return(out)
}
h <- 1e-08
psi.hessian <- function(psi, y, a, b, p1, p2) {
  const = sum(y^2)*(-b/a)*2
  out = const-(p1-1)/(psi+1)^2-(p2-1)/(1-psi)^2
  return(out)
}

#Iteration 1
barmu[1] = 1/T*(sum(y[2:T]) + yhat0 - psi0*sum(y))
lambda[1] = b0/(a0*T)
hatpsi[1] = optimise(psi.k, c(0, 1), y, a0, b0, yhat0, barmu0, p1, p2, maximum=TRUE)$maximum
gamma[1] = -1/(psi.hessian(psi0, y, a0, b0, p1, p2))
a = (T-2)/2
b[1] = 1/2*(sum(y[2:T]^2-2*y[2:T]*(barmu0+psi0*y[1:(T-1)])) + T*(barmu0^2+lambda0) +
            sum((psi0^2+gamma0)*y[1:T]^2+2*barmu0*psi0*y[1:T]) + yhat0^2+d0-2*yhat0*(barmu0+psi0*y[T]))
yhat[1] = barmu0 + psi0*y[T]
d[1] = b0/a0

#Loop
for(i in 2:N){
  barmu[i] = 1/T*(sum(y[2:T]) + yhat[(i-1)] - hatpsi[(i-1)]*sum(y))
  lambda[i] = b[(i-1)]/(a*T)
  hatpsi[i] = optimise(psi.k, c(0, 1), y, a, b[(i-1)], yhat[(i-1)], barmu[(i-1)], p1, p2, maximum=TRUE)$maximum
  gamma[i] = -1/(psi.hessian(hatpsi[(i-1)], y, a, b[(i-1)], p1, p2))
  b[i] = 1/2*(sum(y[2:T]^2-2*y[2:T]*(barmu[(i-1)]+hatpsi[(i-1)]*y[1:(T-1)])) + T*(barmu[(i-1)]^2+lambda[(i-1)]) +
                sum((hatpsi[(i-1)]^2+gamma[(i-1)])*y[1:T]^2+2*barmu[(i-1)]*hatpsi[(i-1)]*y[1:T]) +
                yhat[(i-1)]^2+d[(i-1)]-2*yhat[(i-1)]*(barmu[(i-1)]+hatpsi[(i-1)]*y[T]))
  yhat[i] = barmu[(i-1)] + hatpsi[(i-1)]*y[T]
  d[i] = b[(i-1)]/a
}
support <- seq(-1, 8, 0.005)
dens <- dnorm(support, yhat[N], sqrt(d[N]))
@

A Metropolis Hastings MCMC scheme was set up using a random walk candidate distribution for $\psi$ to draw from $p(\mu | y_{1:T}), p(\sigma^2 | y_{1:T})$ and $p(\psi | y_{1:T})$. These draws were then used to find the Rao-Blackwellised distribution of $p(y_{T+1} | y_{1:T})$.
The chain had 1000 burn in draws followed by 50000 kept draws and took 6.736 seconds to complete the chain and forecast distribution.
<<mcmc, echo=FALSE>>=
##MCMC
B <- 1000
K <- 50000
chain <- matrix(0, ncol=3, nrow=(B+K))
mu0 = 1
sig0 = 1
psi0 = 0.8

psi.kmcmc <- function(psi, mu, sigma2, y, p1, p2) {
  out = -1/(2*sigma2)*sum((y[2:T]-(mu+psi*y[1:(T-1)]))^2) + (p1-1)*log((1+psi)/2) + (p2-1)*log((1-psi)/2)
  return(exp(out))
}

#Starting iteration
mubar = sum(y[2:T]-chain[1,2]*(y[1:(T-1)]))/T
chain[1,1] = rnorm(1, mubar, sqrt(sig0/T))
old = psi0
candidate = rtruncnorm(1, -1, 1, old, 0.15)
alpha = psi.kmcmc(candidate, chain[1,1], sig0, y, p1, p2)/dtruncnorm(candidate, -1, 1, old, 0.15)/
        (psi.kmcmc(old, chain[1,1], sig0, y, p1, p2)/dtruncnorm(old, -1, 1, candidate, 0.15))
alpha = min(alpha, 1)
test = runif(1)
if(alpha > test) {
  chain[1,2] = candidate
} else {
  chain[1,2] = old
}

chain[1,3] = 1/rgamma(1, shape=(T-1)/2, rate=sum((y[2:T]-(chain[1,1]+chain[1,2]*y[1:(T-1)]))^2)/2)

#Loop
for(i in 2:(B+K)) {
  mubar = sum(y[2:T]-chain[(i-1),2]*(y[1:(T-1)]))/T
  chain[i,1] = rnorm(1, mubar, sqrt(chain[(i-1),3]/T))
  old = chain[(i-1),2]
  candidate = rtruncnorm(1, -1, 1, old, 0.15)
  alpha = psi.kmcmc(candidate, chain[1,1], sig0, y, p1, p2)/dtruncnorm(candidate, -1, 1, old, 0.15)/
         (psi.kmcmc(old, chain[1,1], sig0, y, p1, p2)/dtruncnorm(old, -1, 1, candidate, 0.15))
  alpha = min(alpha, 1)
  test = runif(1)
  if(alpha > test) {
    chain[i,2] = candidate
  } else {
    chain[i,2] = old
  }
  chain[i,3] = 1/rgamma(1, shape=(T-1)/2, rate=sum((y[2:T]-(chain[i,1]+chain[i,2]*y[1:(T-1)]))^2)/2)
}

ypred = data.frame(support = seq(-1, 8, 0.005))
ypred$density = rao(chain[1001:51000,], ypred$support, 50000, y[T])
@
\begin{figure}[hb]
\centering
<<plots, echo=FALSE, fig=TRUE>>=
densities <- cbind(q = dens, p = ypred$density)
ggplot() + geom_line(data=data.frame(sup=support, dens=dens), aes(x=sup, y=dens), colour="blue") + theme_bw() + 
  geom_line(data=data.frame(s = support, d = ypred$density), aes(x=s, y=d), colour="red") + labs(x="Support", y="Density")
@
\caption{Variational approximation for $q(y_{T+1}|y_{1:T})$ (blue) and the MCMC density for $p(y_{T+1}|y_{1:T})$ (red). 
The KL Divergence from q to p is 0.0049, and from p to q is 0.0056.}
\label{densities}
\end{figure}

>>>>

\documentclass{article}
\usepackage{natbib}
\usepackage{color}
\usepackage[dvipsnames,svgnames*]{xcolor}
\usepackage{array}
\usepackage[colorlinks=TRUE, linkcolor=blue]{hyperref}
\usepackage{wrapfig,float}
\usepackage[font=small,skip=5pt]{caption}
\usepackage[aboveskip=2pt]{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{ulem}
\usepackage[section]{placeins}
\usepackage{afterpage}
\usepackage{bbm}
\usepackage{Sweave}
\begin{document}
\input{ar1_predictive-concordance}

@@

A Metropolis Hastings MCMC scheme was set up using a random walk candidate distribution for $\psi$ to draw from $p(\mu | y_{1:T}), p(\sigma^2 | y_{1:T})$ and $p(\psi | y_{1:T})$. These draws were then sampled to find the distribution of $p(y_{T+1} | y_{1:T})$.
The chain had 1000 burn in draws followed by 50000 kept draws and took 6.736 seconds to complete the chain and forecast distribution.

\begin{figure}[hb]
\centering
\includegraphics{ar1_predictive-plots}
\caption{Variational approximation for $q(y_{T+1}|y_{1:T})$ (blue) and the MCMC density for $p(y_{T+1}|y_{1:T})$ (red). 
The KL Divergence from q to p is 0.015, and from p to q is 0.018.}
\label{densities}
\end{figure}
